Descriptivas

### 2021-01-26 tarea_2/tarea_2.Rmd
Update tarea_2.Rmd

#paquetes sam
library(readr)
library(dplyr)
library(splitstackshape)
library(corrplot)
library(ggplot2)
library(viridis)
library(viridisLite)
library(hrbrthemes)
library(tidyr)
library(CGPfunctions)
library(arsenal)
library(table1)
library(kableExtra)
library(stargazer)

>>>>

#paquetes sam
library(readr)
library(dplyr)
library(splitstackshape)
library(ggplot2)
library(viridis)
library(viridisLite)
library(hrbrthemes)
library(tidyr)
library(table1)
library(kableExtra)
